%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{kafka_resume}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Kafka Reyya} & Last Updated : June 10, 2019\\
  {PhD candidate, at Waterloo Physics Intellligence Lab} & email: \href{mailto:kafka.reyya@gmail.com}{kafka.reyya@gmail.com} \\
  {Department of Physics, University of Waterloo, Waterloo, Canada} & web: \href{https://www.kafkablogs.com}{kafkablogs.com} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart

     \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {PhD candidate; }{Since Aug. 2018}
    \resumeSubheading
      {University of Waterloo}{Waterloo, Canada}
      {Master of Science in Physics;  GPA: 4.00 / 4.00}{Aug. 2015 -- Dec. 2017}
    \resumeSubheading
      {University of Indonesia}{Depok, Indonesia}
      {Bachelor of Physics;  GPA: 3.96 / 4.00}{Aug. 2011 -- July. 2015}
      
\resumeSubHeadingListEnd
  
%  -----------PUBLICATION---------------
\section{Publications (5 Selected Publications)}
\resumeItemListStart
  
    \publicationItem
    		{First Author, Second Author, Third Author, etc.}{Papers Title Here}{Journal Here}{2019}
    \publicationItem
    		{Kafka R., Doe J., Emilia C., Alexander T.}{Superficial Neural Network for Analytical Continuation}{Phys. Rev. Lett.}{2019}
    \publicationItem
    		{Alexander T., Emilia C., Kafka R.,}{New Method on Fast Learning Monte Carlo}{Journal of Condensed Matter Physics.}{2018}
    \publicationItem
    		{Kafka R., Alexander T.}{Dynamical Mean Field Theory for Boson}{Phys. Rev. E.}{2018}
    \publicationItem
    		{Wellings M., Kafka R., Alexander T.}{Thermoelectric of Strongly Correlated System}{APS March Meetings.}{2017}    		    		    		
\resumeItemListEnd

Full Publications: \href{https://scholar.google.ca/citations?hl=en&user=lyMGnwIAAAAJ}{https://scholar.google.ca/citations?hl=en\&user=lyMGnwIAAAAJ} 

%-----------EXPERIENCE-----------------
\section{Professional Experience}
\resumeSubHeadingListStart

    \resumeSubheading
      {Google}{Mountain View, CA}
      {Data Scientist}{Jan - Sept 2018}
      \resumeItemListStart
        \resumeItem{Tensorflow}
          {TensorFlow is an open source software library for numerical computation using data flow graphs; primarily used for training deep learning models.}
        \resumeItem{Apache Beam}
          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines, as well as a set of language-specific SDKs for constructing pipelines and runners.}
      \resumeItemListEnd

    \resumeSubheading
      {Indonesian Institute of Sciences}{Depok, Indonesia}
      {Intern Researcher}{Jan - June 2015}
      \resumeItemListStart
        \resumeItem{High Energy Physics Modelling}
          {Modelling Cross-Section of Kaon Particle with Strange Electromagnetic Force with Python and C++ and numerous scientific libraries}
        \resumeItem{Mathematical Analysis of CERN Data}
          {Analysis the Cross-Section data of Kaon particle from CERN database.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{ALPS v2.0 Libraries}
      {Contributed to ALPS Physics Libraries for DMFT calculation}{https://github.com/ALPSCore/ALPSCore}
    \resumeSubItem{TRIQS v2.1 Libraries}
      {Contributed to ALPS Physics Libraries for MaxEnt analytical calculation}{https://github.com/TRIQS/triqs}
    \resumeSubItem{Tight Binding of Topology Material}
      {Initiate Tight Binding Software Libraries in calculation of topological effect}{https://github.com/TightBinding}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd
  
  
 %-----------PROJECTS-----------------
\section{Awards and Scholarship}

\resumeItemListStart

	\dottedItem{Best Speaker on ISCPMS 2019}{2019}
	\dottedItem{Canada Foreign Student Scholarship}{2018 - present}
	\dottedItem{LPDP Indonesia}{2015 - 2017}

\resumeItemListEnd


%-----------PROJECTS-----------------
\section{Talks}

\resumeItemListStart

	\dottedItem{ISCPMS 2019}{Feb 12, 2019}
	\dottedItem{APS March Meetings}{March 22, 2018}
	\dottedItem{Confrence on Mathematical Physics}{Sept 02, 2015}
	\dottedItem{Guest Lecturer on Introduction of Many Body Physics}{July 20, 2015}
	\dottedItem{Emacs Confrence, "How to use proper emacs"}{June 13, 2014}

\resumeItemListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Miscellaneous}
 \resumeSubHeadingListStart
 
   \item{ \textbf{Teaching Assitant (TA) :} \\
	\listItem{Continuos Quantum Monte Carlo, 2019 (M.Sc Physics., Georgia Institue of Technology)}
	\listItem{Machine Learning for Dummies, 2016 (B.Sc Physics., University of Waterloo)}
	\listItem{Mathematical Physics I, 2014 (B.Sc Physics., Universitas Indonesia)}
   }
   
   \item{ \textbf{Lab Assistant (TA) :} \\
	\listItem{Optical Tweezers Lab, 2019 (M.Sc Physics., Georgia Institue of Technology)}
	\listItem{ARPES lab, 2014 (B.Sc Physics., University of Waterloo)}
   }
   
   \item{ \textbf{Thesis Supervision :} \\
	\listItem{John Doe, 2019 (M. Sc Physics., ongoing)}
	\listItem{Sulaeman Bona, 2014 (Bachelor Physics., 2014)}
   }
   
   \item{ \textbf{Technical Skills} \\
	\listItem{Linux Distribution Development}
	\listItem{Language: Julia, Fortran, C++, JavaScript}
	\listItem{HPC: MPI, JuliaDistributed, OpenMP, Job Distribution and Nodes.}
	\listItem{Web Development: HTML5, CSS, ReactJS, Bootstrap, Django}
	\listItem{Tools: Linux, Git, Emacs, Vim}
   }
   
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
